Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-05-19 main.tex
added new plot for accuracy vs resolution

Previous publications used a hard threshold on the number of subjects kept for the recognition
stage as a compromise between recognition speed and potential recognition rate.
In order to better motivate 
a choice for a threshold of the number of users kept for the recognition stage,
we varied the number of users kept for the recognition stage and estimated the probability
of the test user being among the set of training users kept for the recognition stage.
As can be seen in Figure \ref{fig:user_alignment_rank_plot}, there are rapidly diminishing
returns as the number of kept users is increased beyond ten.  
\begin{figure}
\centering
\includegraphics[width=3.4in]{figures/user_alignment_rank_plot}
\caption{Probability of the test user being kept for the recognition stage vs. Number of traning
users kept for the recognition stage}
\label{fig:user_alignment_rank_plot}
\end{figure}

@@

\subsection{Face Recognition Pipeline Benchmarks}
\label{sec:pipeline_benchmark}
The fourth experiment compares the recognition rate of the face recognition algorithm at different
image resolutions.  We fixed the number of users to be $enter here$ which was shown in figure  $enter here$  have 95\% probability
to have the true user in the training set, inner loop tolerance to 1e-2 and outer loop tolerance to 1e-3.

>>>>

Previous publications used a hard threshold on the number of subjects kept for the recognition
stage as a compromise between recognition speed and potential recognition rate.
In order to better motivate 
a choice for a threshold of the number of users kept for the recognition stage,
we varied the number of users kept for the recognition stage and estimated the probability
of the test user being among the set of training users kept for the recognition stage.
As can be seen in Figure \ref{fig:user_alignment_rank_plot}, there are rapidly diminishing
returns as the number of kept users is increased beyond 20.  
\begin{figure}
\centering
\includegraphics[width=3.4in]{figures/user_alignment_rank_plot}
\caption{Probability of the test user being kept for the recognition stage vs. Number of traning
users kept for the recognition stage}
\label{fig:user_alignment_rank_plot}
\end{figure}

@@

\subsection{Face Recognition Pipeline Benchmarks}
\label{sec:pipeline_benchmark}
The fourth experiment compares the recognition rate of the face recognition algorithm at different image resolutions.  We tested 5 square resolutions {32, 48, 64, 96, 128} with no image perturbations.  We fixed the number of users to 20 which was shown in figure \ref{fig:user_alignment_rank_plot} have approximately 95\% probability to have the true user in the training set, inner loop tolerance to 1e-5 and outer loop tolerance to 1e-2.

\begin{figure}
\centering
\includegraphics[width=3.4in]{figures/accuracyVsResolution}
\caption{Accuracy vs Image Resolution}
\label{fig:accuracy_vs_resolution}
\end{figure}

The results shown in figure \ref{fig:accuracy_vs_resolution} indicate that
image resolutions of 64x64 provides the best recognition rate for our pipeline. One possible reason why the higher resolutions have a lower recognition rate is that the higher resolution images may contain more noise.
